**Generalized additive models to analyze biomedical non-linear longitudinal data in R: Beyond repeated measures ANOVA and Linear Mixed Models**

### 2021-11-09 Manuscripts/Manuscript_by_chapters-SIM_Revisions/sections/02-Challenges.Rmd
Working on GLM and GLMM section

>>>>

# The contemporary statistical landscape

We consider that a proper understanding of GAMs would be incomplete without a brief survey of contemporary statistical models. Particularly because it seems to be a disconnect between biomedical research and the current state of Statistics. Today, the Statistical landscape has changed drastically and yet, biomedical research at large continues to be confined to a 't-test', 'ANOVA' mentality. The shortcomings that such view produces cannot be properly addressed without a brief mention of statistical methods.

In contemporary Statistics,

## Generalized linear models (GLM)

Need the two first equations

$$y_{ijt} \sim \mathcal{D}(\mu_{ijt},\phi)$$

$$E(y_{ijt})=\mu_{ijt}=g^{-1}(\eta_{ijt})$$

and this one

$\eta_{ijt}=\beta_0+\beta_1x_{ijt}$ This is the GLM

## Generalized linear mixed models (GLMMs)

$\eta_{ijt}=\beta_0+\beta_1x_{ijt}+\mu_{ij}$ GLMM
